1.3: Meet R

### 2019-09-03 content/reading/03-reading.Rmd
Fix reading and tweak slides for class 3

- <i class="fas fa-external-link-square-alt"></i>@R4DS[Ch. 1] 1^[[https://r4ds.had.co.nz/introduction.html](https://r4ds.had.co.nz/introduction.html)]

Now that we start working with R, we will

>>>>

- <i class="fas fa-external-link-square-alt"></i>Ch.1^[http://r4ds.had.co.nz/introduction.html] in @R4DS[Ch. 1]

Now that we start working with R, you should consider this book to be your primary reference for R-related questions. We will broadly cover the first few chapters in order over the next 2-3 class periods.

### 2019-09-03 static/slides/03-slides.Rmd
Fix reading and tweak slides for class 3

---
title: "1.3: Meet R"
subtitle: "ECON 480 · Econometrics · Fall 2019"
author: 'Ryan Safner<br> Assistant Professor of Economics <br> <a href="mailto:safner@hood.edu"><i class="fa fa-paper-plane fa-fw"></i> safner@hood.edu</a> <br> <a href="https://github.com/ryansafner/metricsf19"><i class="fa fa-github fa-fw"></i> ryansafner/metricsf19</a><br> <a href="https://metricsF19.classes.ryansafner.com"> <i class="fa fa-globe fa-fw"></i> metricsF19.classes.ryansafner.com</a><br>'
#date:
output:
  xaringan::moon_reader:
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML" # rescales math with css changes https://github.com/yihui/xaringan/issues/143
    lib_dir: libs
    #seal: false
    css: [custom.css, custom-fonts.css, "hygge"] #, metropolis, metropolis-fonts
    nature:
      beforeInit: ["macros.js", "https://platform.twitter.com/widgets.js"] # first is for rescaling images , second is for embedding tweets, https://github.com/yihui/xaringan/issues/100
      highlightStyle: github #ocean rainbow #monokai rainbow solarized-light #tomorrow-night -blue -eighties zenburn
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
    includes:
      in_header: header.html # for font awesome, used in title  
---

@@

- R itself is just a command language 
    - The `R` *app* is basically just a command line
    - You can even just use your computer's command line!<sup>.red[2]</sup>
]

@@

- R Studio has 4 window panes:
    1. **Source**<sup>.red[1]</sup>: a text editor for documents, R scripts, etc.
    2. **Console**: type in commands to run
    3. **Browser**: view files, plots, help, etc
    4. **Environment**: view created objects, command history, version control

@@

- .font130[.onfire[You don't "learn R, you learn how to do things in R]]

@@

- Today may seem a bit overwhelming
    - You don't need to know or internalize all of this today
    - Use this as a reference to come back to over the semester
    - Last year I started making [a partial book](http://ryansafner.com/tutorial/r4eh), I may revive it

@@

- type `help(function_name)` or `?(function_name)` to get documentation on a function
.center[
![:scale 50%](http://socviz.co/assets/ch-09-read-a-help-page.png)

From Kieran Healy's excellent (free online!) [book on Data Visualization](http://socviz.co/).]
]
---

@@

- Not relevant yet, but once we start writing longer blocks of code, it helps to have a consistent (and human-readable!) style
    - I follow [this style guide](http://adv-r.had.co.nz/Style.html) (you are not required to)<sup>.red[1]</sup>

@@

.footnote[<sup>.red[1]</sup> Also described in [today's course notes page](http://metricsf19.classes.ryansafner.com/class/03-class/) and the course [reference page](http://metricsf19.classes.ryansafner.com/reference.

@@

.pull-left[
- R is an "**object-oriented**" programming language
- 99% of the time, you will be:

@@

```{r}
# make two vectors
fruits<-c("apple","orange","pear","kiwi","pineapple")
numbers<-c(3.3,2.0,6.1,7.5,4.2)

@@

class: inverse, center, middle
# Resources

>>>>

---
title: "1.3: Meet R"
subtitle: "ECON 480 · Econometrics · Fall 2019"
author: 'Ryan Safner<br> Assistant Professor of Economics <br> <a href="mailto:safner@hood.edu"><i class="fa fa-paper-plane fa-fw"></i> safner@hood.edu</a> <br> <a href="https://github.com/ryansafner/metricsf19"><i class="fa fa-github fa-fw"></i> ryansafner/metricsf19</a><br> <a href="https://metricsF19.classes.ryansafner.com"> <i class="fa fa-globe fa-fw"></i> metricsF19.classes.ryansafner.com</a><br>'
#date:
output:
  xaringan::moon_reader:
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML" # rescales math with css changes https://github.com/yihui/xaringan/issues/143
    lib_dir: libs
    #seal: false
    css: [custom.css, custom-fonts.css, "hygge"] #, metropolis, metropolis-fonts
    nature:
      beforeInit: ["macros.js", "https://platform.twitter.com/widgets.js"] # first is for rescaling images , second is for embedding tweets, https://github.com/yihui/xaringan/issues/100
      highlightStyle: solarized-dark #ocean rainbow #monokai rainbow solarized-light #tomorrow-night -blue -eighties zenburn
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
    includes:
      in_header: header.html # for font awesome, used in title  
---

@@

- R itself is just a command language 
- The `R` *app* is basically just a command line, you can even just use your computer's command line!<sup>.red[2]</sup>
]

@@

R Studio has 4 window panes:

1. **Source**<sup>.red[1]</sup>: a text editor for documents, R scripts, etc.
2. **Console**: type in commands to run
3. **Browser**: view files, plots, help, etc
4. **Environment**: view created objects, command history, version control

@@

- .font130[.onfire[You don't "*learn R*", you learn *how to do things in R*]]

@@

- .whisper[Today may seem a bit overwhelming]
    - You don't need to know or internalize all of this today
    - Use this as a reference to come back to over the semester
    - Last year I started making [a partial book](http://ryansafner.com/tutorial/r4eh), I may revive it

@@

- type `help(function_name)` or `?(function_name)` to get documentation on a function
.center[

From Kieran Healy's excellent (free online!) [book on Data Visualization](http://socviz.co/).]

![:scale 50%](http://socviz.co/assets/ch-09-read-a-help-page.png)

@@

- Once we start writing longer blocks of code, it helps to have a consistent (and human-readable!) style
- I follow [this style guide](http://adv-r.had.co.nz/Style.html) (you are not required to)<sup>.red[1]</sup>

@@

.footnote[<sup>.red[1]</sup> Also described in [today's course notes page](http://metricsf19.classes.ryansafner.com/class/03-class/) and the course [reference page](http://metricsf19.classes.ryansafner.com/reference).

@@

.pull-left[
- R is an .shout[**object-oriented**] programming language
- 99% of the time, you will be:

@@

.pull-right[
```{r}
# make two vectors
fruits<-c("apple","orange","pear","kiwi","pineapple")
numbers<-c(3.3,2.0,6.1,7.5,4.2)

@@
